\textbf{M. Shimizu} | Junior Software Engineer \hfill October 2025 -- Present \\ % [cite: 36, 38]
\vspace{-0.4cm}
\begin{itemize}[leftmargin=*, noitemsep]
    \item Led the TPC Facelift project, developing event-driven backend modules with Java, Quarkus, and Vert.x for real-time industrial tool telemetry at Volkswagen assembly lines. % [cite: 39]
    \item Developed reactive RESTful APIs for asynchronous processing of high-volume manufacturing data using Hibernate Reactive for Volkswagen, Scania, and GM. % [cite: 40]
    \item Optimized deployment cycles and standardized client server environments by containerizing .NET enterprise applications utilizing native Windows Containers in Docker. % [cite: 41]
    \item Ensured high availability and system resilience through automated testing pipelines using JUnit, Mockito, and Gatling. % [cite: 42, 43]
\end{itemize}

\textbf{Federal University of ABC (CNPq)} | Machine Learning Researcher \hfill September 2024 -- Present \\ % [cite: 46, 47, 48]
\vspace{-0.4cm}
\begin{itemize}[leftmargin=*, noitemsep]
    \item Develops predictive models focused on biometric authentication via typing dynamics and fingerprints, aiming for state-of-the-art accuracy levels. % [cite: 32, 51, 52]
    \item Applies Convolutional Neural Networks (CNNs) and DeepPrint architectures for feature extraction utilizing PyTorch and Keras. % [cite: 53, 59]
\end{itemize}

\textbf{Evo Systems} | Trainee Systems Analyst / Software Engineer \hfill July 2021 -- February 2024 \\ % [cite: 65, 67, 69, 78, 79]
\vspace{-0.4cm}
\begin{itemize}[leftmargin=*, noitemsep]
    \item Designed and maintained .NET/C\# REST APIs, executing AWS integrations (SES, S3) and complex relational database queries via EF Core. % [cite: 70, 71]
    \item Integrated AWS Lambda and Amazon Rekognition for facial recognition access control systems for BASF. % [cite: 77]
    \item Built cross-platform Flutter applications with Firebase integrations and real-time Bluetooth data processing. % [cite: 72, 73, 74]
\end{itemize}
